Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-25 doc/main_jfm.tex
touched up intro

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and formulating it in a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

@@

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a Janus-vesicle behaves like
a vesicle in these flowing conditions. In particular, we show that a
Janus-vesicle undergoes tank-treading in a shear flow and vertical
migration in a channel flow. Furthermore we use the hybrid continuum
model to investigate the inter-leaflet slippage and rupture of a bilayer
membrane due to an imposed flow. Finally, we compare a pair of
interacting Janus-vesicles with a continuum model of a pair of vesicles.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}), which
guarantee that the suspension remains contact-free. These methods do not
introduce stiffness, but potentially expensive nonlinear complementarity
problems must be solved at each time step.  Repulsion-based contact
methods, which we employ, introduce an artificial repulsion force that
increases in strength as two particles approach one another
(\cite{glo-pan-hes-jos-per2001, fen-mic2004, kab-qua-bir2018}). Strong
repulsion forces can introduce numerical stiffness, but with the
presence of the hydrophobic forces, we maintain a contact-free
suspensions with a relatively weak non-stiff repulsive force.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{validation} we present validation of our model, and in
\S~\ref{results} we present simulation results for a single and pair of
Janus-vesicles under various flowing conditions. Finally we provide
discussion and outlook for future directions in \S~\ref{conclusion}.

>>>>

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

@@

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a Janus-vesicle behaves like
a vesicle in these flowing conditions. In particular, we show that a
Janus-vesicle undergoes tank-treading in a shear flow and vertical
migration in a Poiseuille flow. Furthermore we use the hybrid continuum
model to investigate the inter-leaflet slippage and rupture of a bilayer
membrane due to an imposed flow. Finally, we compare a pair of
interacting Janus-vesicles with a continuum model of a pair of vesicles.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but potentially expensive nonlinear
complementarity problems must be solved at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively weak non-stiff repulsive
force.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{validation} we validate our model, and in \S~\ref{results} we
present simulation results for a single and pair of Janus-vesicles under
various flowing conditions. Finally we provide discussion and outlook
for future directions in \S~\ref{conclusion}.
